---
title: "Assignment1 Submission"
autor: "V Sai Pranav - U01783582"
output: html_document
---

## Answers


**1.** 
```{r}
mileage <- c(65311 , 65624 , 65908 , 66219 , 66499 , 66821 , 67145 , 67447 )
mileage
```

**a.** 
```{r}
#diff : 
diff(mileage, lag = 2, differences = 1)
```
Based on the result above, I think the diff() function is used to find the difference between each consecutive pair. In above code lag=2 means the difference is calculated between 1st and 3rd values, then 2nd and 4th values and so on and differences =1 means diff() is called once on a vector.


**b.** 
```{r}
#length :
length(mileage)
```
This particular result gives us the actual length of the vector mileage


```{r}
length(mileage) <- 3      
mileage 
```

This result of length sets the length of vector mileage to 3
So basically length() is used to get or set the value of a vector.


**c.** 
```{r}
mean(mileage)
max(mileage)
min(mileage)
sd(mileage)
```


**2.** 
    
**a.**  
```{r}
commute <- c(17, 16, 20, 24, 22, 15, 21, 15, 17, 22)
commute                 # Gives us the vector with times in minutes
mean(commute)           # tells the mean vector commute
summary(commute)        # gives the statistical summary of vector commute
```

**b.** 
```{r}
commute[4] = 18
commute                   # new value has been assigned
```


```{r} 
mean(commute)   #new mean of commute
```

**c.**
```{r}
commute[commute>=20] # as you can see our commute was more than or equal to 20, 4 times
```


**d.**  
```{r}
commute[commute<17]   # There are 3 values less than 17 
```
```{r}
x=length(commute[commute<17])         # length of values are stored in vector x which is less than 17
x
y=length(commute)                  # Total length of values is stored in the vector y
y
z = x/y*100                     # Here we have done basic percentage calculation to get the percentage which is 30
z
```

**e.**

```{r}
commute + 1
```
The function above adds one to all the values in the vector.

```{r}
commute[-6]
```
The function above gives us all the values but not the value in which has an index of 6.

```{r}
sum(commute>21 | commute<16) 
```
The function above will first check for the values that are greater than 21 or less than 16. Since |(or) is a logical operation it will either give True(1) or False(0). As a result we got sum as 4 which means that there are 4 True(1) in the condition inside sum.

```{r}
commute[commute>=17]
```
The function above will give us all the values in commute that are greater than or equal to 17

```{r}
sum(commute[commute>20])
```
The function above gives us the sum of all the values in commute which are greater than 20
```{r}
commute[4:6] 
```
The function above will give us all the values in commute which are in index 4 to index 6


**3.**
```{r}
x = c(1,2,3,4,5,6,6,7,7,9)      # As the data for 3rd question is not visible in the questions I have considered the following data and done the computations as asked.
x
length((x))               
```
**a.**
```{r}
sum(x)/10    # This command will give us 5 because sum(x) = 50, and if we divide 50 by 10 answer is 5.
```
**b.**
```{r}
log10(x)
#OR
log10(x[1:10])   #Both of the commands will give the same output. It is up-to the user which one you want to use.
```
**c.**
```{r}
(x^4.4)/2.875
#OR 
(x[1:10]^4.4)/2.875     #Both of the commands will give the same output. It is up-to the user which one you want to use.
```
**d.**
```{r}
max(x)   # will give maximum value in vector x
min(x)   # will give minimum value in vector x
a = max(x) - min(x)
a         # The difference between maximum value am minimum value in x is stored in "a"
```


**4.** 
  **a.** 
  
```{r}
bill = c(46, 33, 39, 37, 46, 30, 48, 32, 49, 35, 30, 48)
bill
range(bill)         # gives maximum and minimum values
range(bill)[1]       # gives minimum value
range(bill)[2]       # gives maximum value
range(bill)[2]-range(bill)[1]   # gives the difference between maximum and minimum value.
```
The function above will give the maximum and minimum values in the given vector, we can use the same function to solve the last question in 3rd question.

  **b.** 
  
```{r}
bill[bill>40]   # As we can see the bill was greater than 40 for 5 months.
```
```{r}
x=length(bill[bill>40])         # length of values are stored in vector x which are greater than 40
x
y=length(bill)                  # Total length of values is stored in the vector y
y
z = x/y*100                     # Here we have done basic percentage calculation to get the percentage which is 41.66667
z
```

