---
title: "IS-680_FALL_MIDTERM_V_SAI_PRANAV"
output: html_notebook
---


```{r}
require(tidyverse)
movies=read_csv(url('https://ygenc.github.io/lectures/data/movies.csv'))
```
Loading the data

```{r}
movies
```
**QUESTION_1**

**A**
```{r}
glimpse(movies)
```
```{r}
str(movies)
```
As we have used str() and glimpse we can see the datatypes of the columns in movies.

```{r}
names(movies)
```
**B**
```{r}
ncol(movies)
```
With ncol() we can check the number of the columns in the dataframe

```{r}
nrow(movies)
```
With nrow() we can check the number of the rows in the dataframe

**C**
```{r}
movies_1 <- movies
```
making copy of data frame so that actual data does not affect

```{r}
category <- cut(movies_1$budget_2013, breaks = 3, labels = c("low","medium","high"))
table(category)
```
As you can see above, We have used cut() function in-order to transform the numerical value to categorical value by dividing the budget_2013 to low budgeted, medium budgeted and high budgeted films.

```{r}
movies_1$budget_2013[1:10]
```


```{r}
category[1:10]
```
The above two chucks compares the first 10 rows that are in numerical and categorical format.


**QUESTION2**

**A**
```{r, warning=FALSE}
ggplot(movies, aes(x = budget_2013, fill = binary)) +
  geom_histogram(position = "dodge",alpha = 0.8) +
  ggtitle("Distribution of Adjusted Budget_2013")
```
In the above graph we have examined the distribution using histograms based on whether the movie has passed or failed the bechdel test.

**B**
```{r, warning=FALSE}
movies_plot <- ggplot(movies, aes(x=domgross,y=intgross)) +
                  geom_point(alpha = 0.9)
movies_plot + labs(title = "relationship between international gross abd domestic gross", 
                   x="domestic gross",y="international gorss")
```
Looking at the graph we can say that there is high correlation between International gross and the domestic gross. Also we have used labs to display the titles.


**C**
```{r, warning=FALSE}
plot_color <- ggplot(movies, aes(x=domgross,y=intgross, color = binary)) +
                  geom_point(alpha = 0.9)
plot_color +  labs(title = "relationship between international gross abd domestic gross", 
                   x="domestic gross",y="international gorss")

```
Here we have passed binary to color aesthetic so that we can see whether the movie has passed or failed.


**D**
```{r, warning=FALSE}

bar_plot <- ggplot(movies_1, aes(x = clean_test, fill = clean_test)) +
              geom_bar() +
              geom_text(stat = 'count', aes(label = ..count..), vjust=2) # This line is to get the count 


bar_plot + labs(title = "Bechdel Test Result without discrepancies", 
                   x="result", y="Count of Respective Category")

```
For this question I opted a bar graph where numerical value is the count and the categorical value is the clean_test column.

  
**QUESTION_3**
**A**
```{r}
library(dplyr)

movies_2000 <- movies %>%
                filter(year > "2000")

movies_2000_cleantest <- select(movies_2000, -clean_test)
movies_2000_cleantest
```

**B**
```{r}
movies_2013 <- movies %>%
                filter(year == "2013")

movies_2013_req <- select(movies_2013, year,title,clean_test,budget_2013:intgross_2013)
movies_2013_req
```

**C**
```{r}
movies_revenue <- movies_2013_req %>%
                    mutate(revenue = (domgross_2013 + intgross_2013) - budget_2013) %>%
                    arrange(desc(revenue)) %>%
                    group_by(title)

movies_revenue

```
The above chunk will give us the calculated revenue column.

```{r}
movies_revenue$title[1:10]
```
As you can see the top 10 movie titles are same that we got in the above chunk


**D**
In this question we will calculate and display the total earnings of the movie.

```{r}
movies_task = movies %>%
                select(year:title,binary,budget_2013:intgross_2013) %>%
                group_by(year) %>%
                mutate(total_earned = domgross_2013 + intgross_2013)

movies_task

```

```{r}
ggplot(movies_task, aes(x=year, y=total_earned, color = year)) +
  geom_point(alpha = 0.9)

```

The above graph displays the total earnings by the movie for the years 1970-2013.


**Question_4**

**A**

```{r}
movies_avg <- movies %>%
                group_by(clean_test) %>%
                summarise(total = n(),
                          avg_budget = mean(budget_2013),
                          avg_domgros = mean(domgross_2013, na.rm = TRUE)) %>%
                mutate(percentage = (total/sum(total))*100)
movies_avg
```


```{r}
movies_pass <- movies %>%
                group_by(year,binary) %>%
                summarise(total = n()) %>%
                mutate(percentage = (total/sum(total))*100) %>% 
                filter(binary == "PASS")
movies_pass
```


**Question_5**

**A**

```{r, warning=FALSE}
plot_color <- ggplot(movies, aes(x=log(budget),y=log(intgross), color = binary, shape = clean_test, alpha = year)) +
                  geom_point() +
                  facet_wrap(~binary)
plot_color + labs(title = "budget VS intgross in Log Scale")
```

**B**

```{r}
movies %>%
  mutate(above_avg_budget = budget_2013 > mean(budget_2013)) %>%
  group_by(above_avg_budget, binary) %>%
  summarize(count = n())

```

As you can see solutions for A,B are the replica of the questions that were asked to do.




