---
title: "IS-680_FALL_FINAL_V_SAI_PRANAV"
output: html_notebook
---

```{r}
require(tidyverse)
```


```{r}
sal_data = read.csv('C:/Users/prana/Desktop/IS-680-R/Project_Datasets/Levels_Fyi_Salary_Data.csv')
sal_data
```

```{r}
names(sal_data)
```


```{r}
ncol(sal_data)
```
Checking for the number of columns

```{r}
nrow(sal_data)
```
Checking for the number of rows

```{r}
summary(sal_data)
```

```{r}
ggplot(sal_data, aes(totalyearlycompensation), fill = title) +
  geom_histogram() +
  facet_wrap(~title)
```

```{r}
ggplot(sal_data, aes(totalyearlycompensation)) +
  geom_boxplot()
```

```{r}
q1 <- quantile(sal_data$totalyearlycompensation, 0.25)
q3 <- quantile(sal_data$totalyearlycompensation, 0.75)
iqr <- IQR(sal_data$totalyearlycompensation)
q1
q3
iqr
```


```{r}
no_outliers <- subset(sal_data, sal_data$totalyearlycompensation > (q1 - 1.5*iqr) & sal_data$totalyearlycompensation < (q3 + 1.5*iqr))
no_outliers
```

```{r}
nrow(sal_data) - nrow(no_outliers)
```


```{r}
ggplot(no_outliers, aes(totalyearlycompensation)) +
  geom_boxplot()
```
Now as you can see in the above boxplot there are no outliers in the column.


```{r}
tot_sal <- sal_data %>%
            group_by(company) %>%
            summarize(tot_salry = sum(totalyearlycompensation)) %>%
            arrange(desc(tot_salry))
tot_sal
```
Here in the chunk above we got the companies that offer more compensation by sorting 'totalyearlycompensation' column.

```{r}
tot_sal$company[1:10]
```
In the above two chunk the Top 10 companies who offer more compensation to their employees has been extracted.

```{r}
lvl_exp <- sal_data %>%
            select(level,yearsofexperience,location) %>%
            mutate(most_exp = yearsofexperience > 40) %>%
            group_by(level, location) %>%
            arrange(desc(most_exp))
            
lvl_exp
```
Displaying the levels which have experience more than 40 years.

```{r}
lvl_exp$level[1:6]
```
Top 6 levels which have an experience of more than 40 years.


```{r}
cmp_bns <- no_outliers %>%
            select(company, bonus) %>%
            group_by(company) %>%
            summarise(total_bns = sum(bonus)) %>%
            arrange(desc(total_bns))
cmp_bns
```
The above chunk elaborates about the companies which gave more bonus compared to other companies in descending order.



```{r}
names(sal_data)
```












