---
title: "Lab_Data Handling_V SAI PRANAV_U01783582"
output: html_notebook
---
```{r}
library(tidyverse)
```

```{r}
library(nycflights13)
```

**Exercise_1**
```{r}
flights
```

```{r}
names(flights)
```
```{r}
glimpse(flights)
```
I have used names and glimpse to explore the data.


**Exercise_2**
```{r, warning=0}
ggplot(flights, aes(dep_delay, fill = carrier)) +
  geom_histogram(position = "dodge",alpha = 0.8, binwidth = 2000)
```
```{r,  warning=0}
ggplot(flights, aes(dep_delay)) +
  geom_histogram()
```
As you can see the difference between plot 1 and plot 2 that we are able to extract information on which flight had more number of delayed departures but in second plot we cannot say that 

**Exercise_3**
```{r,  warning=0}
flights_LAX <- flights %>%
                filter(dest == "LAX")
flights_LAX
```
Here the data set 'flights_LAX' all the info about the flights with the destination = LAX.

```{r,  warning=0}
ggplot(flights_LAX, aes(dep_delay, fill = carrier)) +
  geom_histogram(position = "dodge",alpha = 0.8, binwidth = 200)
```
As you can see clearly that flight carrier "UA" has more number of delays in departure then "AA", and then "VX", so on.

**Exercise_4**
```{r, warning=0}
flights %>%
  group_by(dep_delay) %>%
  summarize(mean_dd = mean(dep_delay),
            median_dd = median(dep_delay),
            n = n())

  
```
Here as you can see we get the mean median as well as th count too.


**Exercise_5**
```{r, warning = 0}
sfo_feb_flights <- flights %>%
                      filter(dest=='SFO', month == 2)
sfo_feb_flights
```
All the data of flights reaching to SFO is in "sfo_feb_flights"

```{r, warning=0}
sfo_feb_flights %>%
  group_by(flight, carrier) %>%
  count(flight) %>%
  arrange(flight)
```
In the above chunk we got the count of the flights going to SFO in a sorted order performed on flights.

**Exercise_6**

```{r}
summary(sfo_feb_flights)
```
As you can see that there are NA's in dep_delay, arr_delay. We have to get rid of them in-order to work with summarize.


```{r, warning=FALSE}
sfo_feb_flights_NA_rem <- na.omit(sfo_feb_flights)
```
I have stored the data frame without NA's into sfo_feb_flights_NA_rem

```{r}
summary(sfo_feb_flights_NA_rem)
```
All the NA's have been removed.

```{r}
sfo_feb_flights_NA_rem %>%
  group_by(carrier) %>%
  summarize(median_dd = median(arr_delay),
            iqr_dd = IQR(arr_delay))
```
The above Output is the median and the iqr grouped by carrier as requested. 

**Exercise_7**

```{r}
summary(flights)
```
We will clear the NA's from the dataframe and store it in a new dataframe as we did earlier.

```{r}
flights_NA_rem <- na.omit(flights)
```

```{r}
summary(flights_NA_rem)
```
As you can see there are no NA's in the new dataframe.


```{r}
flights_NA_rem %>%
  group_by(month) %>%
  summarize(mean_dd = mean(dep_delay))%>%
  arrange(desc(mean_dd))
```
As it was asked in the question to arrange the average in descending order, I have arranged it that way.


**Exercise_8**
```{r}
flights_avg_speed <- flights %>%
                      mutate(avg_speed = distance/(air_time/60))

flights_avg_speed

```
Flights_avg speed has the data with average speed as a new column in it.

**Exercise_9**
```{r,warning=FALSE}
ggplot(flights_avg_speed, aes(avg_speed,distance), color = flight) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  facet_wrap(~carrier)
```
The above graph is faceted based on the carrier so you can see the scatter plots of respective carriers.

